Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-08-02 paper.tex
2Aug refinement v2

\subsection{Stability Selection}
Stability selection is a subsampling strategy with a wide range of applications.  In the context of regularisation methods, it is a way of estimating, 
empirically, the significance of the SNP effects. Compared to permutation the amount of computation is significantly less.  
Analyses are based on only a fraction of the data  and the regularisation parameter need not be optimised.

. We use it for calculating, empirically,  the statistical significance of the SNP effects for the regularisation methods. Unlike permutation, only subsets of the data are drawn for (repeated) analysis. Also, here, 
the regularisation parameter need not be optimised. Instead it can be fixed to a "suitable" value, greatly reducing the amount of computation.

We performed stability selection as follows. For LMM-Lasso and glmnet, we conducted a preliminary analysis to find an 
appropriate value for the regularisation parameter.  We adjusted the parameter so that the analysis yielded 
between 10 to 30 SNPs with non-zero effects. We knew for the simulated data that the number of SNPs in association with the trait followed 
a Poisson distribution with mean 30. In practice, this is obviously unknown. However, stability selection is robust to the number of non-zero effects. 
Any reasonable number here would suffice. 
 We then repeatedly subsampled, without replacement, the data. As recommended \cite{meinshausen2010stability}, we draw 100 subsamples of size $n/2$. Each subsample was analysed with LMM-Lasso and glmnet, with their regularisation parameters fixed.

 We analysed a subsample, with the regularisation parameter  fixed for LMM-Lasso and glmnet.  
 To calculate, empirically,  the statistical significance of each 
SNP across the genome, we counted the number of times a SNP had a non-zero effect size over all the replicates. We then 
divided this number by the number of replicates (which was 100) to form an empirical probability estimate of the significance of a SNP.

>>>>

\subsection{Stability Selection}
Stability selection is a subsampling strategy with a wide range of applications.  In the context of regularisation methods, it is a way of estimating, 
empirically, the significance of the effects. Compared to permutation, the amount of computation is significantly less.  
Analyses are based on only a fraction of the data  and the regularisation parameter need not be optimised.  
To perform stability selection, we did the following.  
For LMM-Lasso and glmnet, the regularisation parameter was fixed to a "suitable" value. This was done  
via a preliminary analysis of the data where we adjusted the regularisation parameter  to yield
between 20 to 30 SNPs with non-zero effect sizes.  Here, the number of non-zero effects is rather arbitrary and any reasonable 
number of non-zero effects would suffice. 
 We then repeatedly subsampled, without replacement, the data. As recommended \cite{meinshausen2010stability}, we drew 100 subsamples of size $n/2$ from the data. Each subsample was analysed with LMM-Lasso and glmnet, with their regularisation parameters fixed. 
A (probability) estimate of the statistical significance of a SNP effect is obtained by counting the 
number of times the SNP had a non-zero effect size over all the replicates divided by the number of replicates (which was 100).

 To calculate, empirically,  the statistical significance of each 
SNP across the genome, we counted the number of times a SNP had a non-zero effect size over all the replicates. We then 
divided this number by the number of replicates (which was 100) to form an empirical probability estimate of the significance of a SNP.
